% Original Template: https://www.overleaf.com/latex/templates/phd-application-cv-template/mrvjhycbdytr

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage[hidelinks]{hyperref} % For hyperlinks
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}
\usepackage{multicol}
\usepackage{blindtext}

% --== Formatting Templates ==--
\titleformat{\section}{\centering\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}
\setlist{noitemsep, nolistsep, rightmargin=1in}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\PresentationItem}[5]{
\noindent\textbf{#1} \hfill \raisebox{\dimexpr-\ht\strutbox+\dp\strutbox\relax}[0pt][0pt]{#2} \\
\underline{#3}
\indent \begin{minipage}{0.6\textwidth} 
\textit{#4} \end{minipage} \hfill #5
\bigskip}

\newcommand{\PresentationItemSmall}[5]{
\noindent\textbf{#1} \hfill #2 \\ 
\underline{#3} 
\indent \textit{#4} \hfill #5
\bigskip}

% For "Knowledge & Skills" lists
\newcommand{\spacedIcon}[1]{\faIcon{#1}\hspace{0.3em}}
\newcommand{\SimpleItem}[2]{ \item[] \noindent\hbox to 0.175\textwidth{{#1}} #2}

% ==================================================================

% Begin document
\begin{document}
\pagestyle{fancy} % Disable page numbers
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[L]{\textit{Michael J. Akinyemi}}
\fancyhead[R]{\textit{June 2025}}
\thispagestyle{empty} % Remove header from the first page


% --== NAME & CONTACT INFO ==--
\begin{center}
\textbf{\Huge Michael J. Akinyemi}\\[6pt]
 \textbf{Phone:} \href{tel:8505531127}{(850) 850-1127} | \textbf{Website:} \href{https://michaelakinyemi.com/}{michaelakinyemi.com} | \textbf{Email:} \href{mailto:mi542876@ucf.edu}{mi542876@ucf.edu}
\end{center}


% --== RESEARCH INTERESTS ==--
\section*{RESEARCH INTERESTS}
\begin{center}
Computational Biology, Immune Engineering, Systems Biology/Immunology, Molecular Biophysics, Autoimmune Disorders, Probabilistic Algorithms, Biostatistics
\end{center}


% --== EDUCATION ==--
\section*{EDUCATION}

\noindent\textbf{University of Central Florida} \hfill Orlando, FL \\
Biomedical Sciences (B.S.) \hfill Spring 2025 \\
Computer Science (Minor) \\
Genomics \& Bioinformatics (Minor)
\begin{itemize}
    \item Ronald E. McNair Scholar
    \item Relevant Coursework:
    \begin{itemize}
        \item \textit{CS: Discrete Structures I, Computer Science II, Computer Logic \& Organization, Object Oriented Programming, Matrix \& Linear Algebra}
        \item \textit{Bio: Immunology, General Microbiology, Biochemistry I, Molecular Biology II, Quantitative Biological Methods}
    \end{itemize}
\end{itemize}
\bigskip

\noindent\textbf{Tallahassee Community College} \hfill Tallahassee, FL \\
Associate of Arts (A.A.) \hfill Summer 2022
\begin{itemize}
    \item Phi Theta Kappa Honors Society
\end{itemize}


% --== RESEARCH EXPERIENCE ==--
\section*{RESEARCH EXPERIENCE}
\noindent\textbf{University of Central Florida} \hfill Orlando, FL\\ 
\textbf{College of Medicine} \hfill December 2023 | Present \\ 
\textbf{Advisor:} Dr. Hung Nguyen \\
\textbf{Research Assistant}
\begin{itemize}
    \item Independently developed a new immune cell datamining pipeline to analyze PBMC scRNA-Seq datasets to discover correlations between metabolic activity and the grafts vs leukemia (GvL) effect.
    \item Investigated correlation between the gut microbiome and immune cell behavior using machine learning models to integrate 16S rRNA-Seq \& various single-cell assays.
\end{itemize} 
\bigskip

\noindent\textbf{Massachusetts Institute of Technology} \hfill Cambridge, MA\\
\textbf{Department of Chemical Engineering} \hfill June 2023 | Present \\
\textbf{Advisor:} Dr. Brandon DeKosky \\
\textbf{Research Intern} $\vert$ MIT Summer Research Program \\
\textit{\underline{Sequential Insertion Project} (Summer 2023)}
\vspace{2mm}
\begin{itemize}
    \item Contributed to a project improving the efficiency of cell line generation for antibody library display systems by reducing the length of the donor plasmid.
    \item Successfully performed troubleshooting of restriction cloning experiments to construct donor plasmid for CRISPR/Cas9-mediated genome integration.
    \item Developed a suite of automated data visualization tools capable of handling high-throughput sequence data.
    \item Optimized clustering algorithms within bioinformatics pipelines to analyze BCR/TCR immune repertoire data collected through NGS, resulting in a >70\% faster runtime.
    \item Developed a novel tool using \textbf{Hidden Markov Models (HMMs)} and probabilistic approaches to correct errors in next-generation sequencing (NGS) of antibody libraries.
\end{itemize}

\vspace{2mm}
\noindent\textit{\underline{Bioinformatics \& HPC Algorithm Optimization }}
\vspace{2mm}
\begin{itemize}
    \item Contributed to a project improving the efficiency of cell line generation for antibody library display systems.
    \item Successfully troubleshot restriction cloning experiments for construction of donor plasmid for CRISPR/Cas9 system.
    \item Optimized clustering algorithms within bioinformatics pipelines to analyze BCR/TCR immune repertoire data collected through NGS.
    \item Developed automated data visualization tools capable of handling high-throughput sequence data.
\end{itemize}


% --== HONORS, AWARDS & SCHOLARSHIPS ==--
\section*{HONORS, AWARDS \& SCHOLARSHIPS}

\noindent\textbf{McNair Summer Research Institute Scholarship}  \hfill Orlando, FL\\ 
\textit{Ronald E. McNair Scholars Program} \hfill {August 2023} \medskip

\noindent\textbf{Conference Presentation Travel Award}  \hfill Orlando, FL\\ 
\textit{UCF Office of Undergraduate Research} \hfill {November 2023} \medskip

\noindent\textbf{Florida Bright Futures Academic Scholars}  \hfill Tallahassee, FL\\
\textit{Florida Department of Education} \hfill {December 2020} \medskip

\noindent\textbf{President's List (3 Times)} \medskip

\noindent\textbf{Dean's List (2 Times)}




% % --== PUBLICATIONS ==--
\section*{PUBLICATIONS}

\noindent \textbf{Akinyemi, M.}, \& DeKosky, B. (1979). \textbf{Probabilistic Approaches to Correct Antibody Library Sequence Errors} Econometrica, 47(2), 263-291. (Published)


% --== PRESENTATIONS ==--
\section*{PRESENTATIONS}

\PresentationItemSmall{Leadership Alliance National Symposium}{Hartford, CT}{Oral}{Probabilistic Approaches to Correct Antibody Library Sequence Errors}{July 2024}

\PresentationItem{UCF Student Scholar Symposium}{Orlando, FL}{Poster}{Overcoming Challenges in CRISPR Vector Restriction Cloning to Optimize Generation of Immune Repertoires.}{March 2024}

\PresentationItem{Annual Biomedical Research Conference For Minoritized Scientists (ABRCMS)}{Phoenix, AZ}{Poster}{Generating a Stable Cell Line: Troubleshooting Restriction Cloning of a CRISPR Vector For Sequential Genome Insertion.}{November 2023}

\PresentationItem{MIT Summer Research Program Fall Extension Research Showcase}{Virtual}{Poster}{Investigating Diversity of V(D)J Gene Recombinants Within Antibody Repertoires}{November 2023}

\PresentationItem{MIT Summer Research Program Showcase}{Cambridge, MA}{Poster}{Generating a Stable Cell Line: Troubleshooting Restriction Cloning of a CRISPR Vector For Sequential Genome Insertion.}{July 2023}

% \PresentationItemSmall{Harvard Medical School Institute for Protein Innovation (IPI)}{Cambridge, MA}{Attendee}{IPI "Surfacing" Symposium on Cell Surface Receptor Biology and Protein Science}{June 2023}






% --== OTHER EXPERIENCES ==--
\section*{OTHER EXPERIENCES}

% \noindent\textbf{Data Science \& Machine Learning Summer Online Program} \hfill Cambridge, MA \\
% Massachusetts Institute of Technology \hfill June 2024 - August 2024
% \begin{itemize}
%     \item Learned formal statistical methods 
% \end{itemize}
% \bigskip

\noindent\textbf{Quantitative Methods Workshop} \hfill Cambridge, MA \\
Massachusetts Institute of Technology \hfill January 2023
\begin{itemize}
    \item Employed principal component analysis (PCA) and k-means clustering to differentiate cells of a scRNA-Seq PBMC data set.
    \item Used machine learning pipelines (CryoSPARC) to generate 3D protein structures from high-framerate movies of CryoEM data.
\end{itemize}
\bigskip

% \noindent\textbf{Florida State University} \hfill Lagos, Nigeria\\ 
% \textit{Department of Urban \& Regional Planning} \hfill December 2019
% \begin{itemize}
%     \item Assisted in data collection
% \end{itemize}

\noindent\textbf{Scripting Team Leader} \hfill Remote \\ 
AvatarMC \hfill May 2017 | June 2022 
\begin{itemize}
    \item Developed both command-line \& GUI-based automation tools to assist workflows of other teams.
    \item Designed quality assurance testing plans for experimental features.
    \item Assisted in writing \& maintaining documentation of in-house scripting language.
    \item Wrote design documents for deliverable requests/feature improvement tasks.
    \item Led projects using professional management software (Phabricator).
    \item Directed team meetings \& effectively delegated tasks.
\end{itemize}



\pagebreak

% --== KNOWLEDGE & SKILLS ==--
\section*{KNOWLEDGE \& SKILLS}


\begin{center}\hspace{2em}
\textbf{Biological Research} \\ \vspace{1.5ex}
Restriction Cloning, Flow Cytometry, Electroporation, Polymerase Chain Reaction (PCR), Gel Electrophoresis, Agarose Gel Extraction, Immunoprecipitation, Cell Culture (Mammalian \& Bacterial), Murine Model Handling, Miniprep/Maxiprep
\hspace{2em}
\end{center}
\bigskip

\hspace{1.5em}
\begin{tabularx}{1\textwidth}{
    >{\raggedright\arraybackslash}X
    >{\raggedright\arraybackslash}X }
    % Row 1
      \textbf{Programming Languages}&   \textbf{Software}\\ 
     \begin{itemize}[leftmargin=.10in]
         \SimpleItem{Python}{Professional.}
         \SimpleItem{R}{Professional.}
         \SimpleItem{C++}{Professional.}
         \SimpleItem{Bash/Shell}{Advanced.}
         \SimpleItem{Java}{Advanced.}
         \SimpleItem{RegEx}{Intermediate.}
     \end{itemize}
     & \begin{itemize}[leftmargin=.10in]
         \SimpleItem{LaTeX}{Professional}
         \SimpleItem{Git}{Professional.}
         \SimpleItem{Slurm}{Advanced.}
         \SimpleItem{SnapGene}{Advanced.}
         \SimpleItem{Docker}{Elementary.}
         \SimpleItem{PyMol}{Elementary.}
      \end{itemize}\\
      
    % Row 2
      \textbf{Operating Systems}&   \textbf{Natural Languages}\\ 
     \begin{itemize}[leftmargin=.10in]
         \SimpleItem{Linux/UNIX}{Professional.}
         \SimpleItem{HPC-Clusters}{Advanced.}
      \end{itemize}
     & \begin{itemize}[leftmargin=.10in]
         \SimpleItem{English}{C2 level.}
         \SimpleItem{Latin}{A2 level.}
         \SimpleItem{Spanish}{A2 level.}
         \SimpleItem{Yoruba}{A1 level.}
      \end{itemize}\\

\end{tabularx}




% --== COMMUNITY INVOLVEMENT ==--
\section*{COMMUNITY INVOLVEMENT}

\noindent\textbf{Society for the Advancement of Chicanos/Hispanics and Native} \hfill Orlando, FL \\ 
\noindent\textbf{Americans in Science (SACNAS)} $\vert$ \textit{Vice President} \hfill April 2024 | Present \\
University of Central Florida
\begin{itemize}
    \item Assisted president in managing club and leading officer meetings.
    \item Held general body meetings discussing tips/advice to help underrepresented students get started in research and the journey to graduate school. 
\end{itemize}

\bigskip

\noindent\textbf{Active Minds} $\vert$ \textit{Secretary} \hfill Orlando, FL \\ 
University of Central Florida \hfill December 2023 | Present
\begin{itemize}
    \item Advocated for mental health and the importance of fighting against the negative stigmas associated with them.
    \item Organized club records, took meeting minutes \& performed general administrative duties. 
\end{itemize}






% \section*{REFERENCES}
% % Shelbe, Brandon, Nguyen


% \begin{tabularx}{1\textwidth}{
%     >{\raggedright\arraybackslash}X
%     >{\raggedright\arraybackslash}X }
%     % Row 1
%       \textbf{Shelbe Johnson} (Graduate Student) &   \textbf{Brandon DeKosky} (Associate Professor)\\ 
%      \begin{itemize}[leftmargin=.10in]
%          \SimpleItem{Python}{Professional.}
%          \SimpleItem{Bash/Shell}{Advanced.}
%      \end{itemize}
%      & \begin{itemize}[leftmargin=.10in]
%          \SimpleItem{LaTeX}{Professional}
%          \SimpleItem{Git}{Advanced.}
%       \end{itemize}\\
      
%     % Row 2
%       \textbf{Operating Systems}&   \textbf{Natural Languages}\\ 
%      \begin{itemize}[leftmargin=.10in]
%          \SimpleItem{Linux/UNIX}{Professional.}
%          \SimpleItem{HPC-Clusters}{Advanced.}
%       \end{itemize}
%      & \begin{itemize}[leftmargin=.10in]
%          \SimpleItem{English}{C2 level.}
%          \SimpleItem{Spanish}{A2 level.}
%       \end{itemize}\\

% \end{tabularx}


% % --== VOLUNTEER EXPERIENCE ==--
% \section*{VOLUNTEER INVOLVEMENT}

% \noindent\textbf{Down Syndrome Foundation} \hfill Orlando, FL \\ 
% \noindent\textbf{in Science (SACNAS) |} \textit{Vice President} \hfill April 2024 | Present \\
% University of Central Florida
% \begin{itemize}
%     \item Assisted president in managing club and leading officer meetings.
%     \item Held general body meetings discussing tips/advice to help underrepresented students get started in research and the journey to graduate school. 
% \end{itemize}

% \bigskip

% \noindent\textbf{Active Minds |} \textit{Secretary} \hfill Orlando, FL \\ 
% University of Central Florida \hfill December 2023 | Present
% \begin{itemize}
%     \item Advocated for mental health and the importance of fighting against the negative stigmas associated with them.
%     \item Organized club records, took meeting minutes \& performed general administrative duties. 
% \end{itemize}



% End document
\end{document}



% TODO:
% try to make the knowledge and skills section more compaect
% add in progress publications
% add more proof of skills
% ask "do they need to see this information"
% independent research section
